\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%------------------------------------
% Custom Commands
%------------------------------------

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2\\
\textit{\small #3} & \textit{\small #4}\\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2\\
\end{tabular*}\vspace{-7pt}
}
% \newcommand{\resumeProjectHeading}[2]{
%     \item
%     \parbox[t]{0.50\textwidth}{\raggedright\small #1}\hfill
%     \parbox[t]{0.46\textwidth}{\raggedleft\footnotesize\itshape #2}\vspace{-7pt}
% }

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------------------------------
%%%%% RESUME STARTS HERE
%------------------------------------

\begin{document}

%------------------------------------
% Heading
%------------------------------------

\begin{center}
\textbf{\Huge Vaibhav Kumar Mahawar}\\ \vspace{1pt}

\small +91-8209851728 $|$
\href{mailto:vaibhavmahawar@rocketmail.com}{vaibhavmahawar@rocketmail.com}
$|$
\href{https://www.linkedin.com/in/vaibhavkumarmahawar}{linkedin.com/in/vaibhavkumarmahawar}
$|$
\href{https://github.com/vaibhavmahawar}{github.com/vaibhavmahawar}
\\
Ajmer, Rajasthan, India
\end{center}
\vspace{-15pt}
%------------------------------------
% Education
%------------------------------------

\section{Education}

\resumeSubHeadingListStart

\resumeSubheading
{Dr. B. R. Ambedkar National Institute of Technology Jalandhar}
{Jalandhar, Punjab}
{Master of Technology in Machine Intelligence and Automation \hfill CGPA: 8.48/10}
{Aug. 2024 -- Jun. 2026}

\resumeSubheading
{Poornima Institute of Engineering and Technology}
{Jaipur, Rajasthan}
{Bachelor of Technology in Computer Science and Engineering \hfill \hspace{7pt} CGPA: 8.54/10}
{Jul. 2019 -- Jun. 2023}

\resumeSubHeadingListEnd
\vspace{-10pt}
%------------------------------------
% Experience
%------------------------------------

\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading
{Software Development Intern}
{Jul. 2022 -- Sep. 2022}
{Techienest Pvt. Ltd.}
{Jaipur, Rajasthan}

\vspace{-4pt}
\resumeItemListStart

\resumeItem{
Developed a React Native mobile application serving 500+ students by integrating REST APIs, progress tracking, and interactive learning modules while improving application usability.
}

\resumeItem{
Collaborated with cross-functional teams to develop, test, and optimize scalable mobile application features while integrating REST APIs and improving application performance and maintainability.
}

\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-13pt}
%------------------------------------
% Projects
%------------------------------------

\section{Projects}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{RudraAI– Intelligent Software Engineering Platform}
$|$
\emph{Node.js, Typescript, Python, Redis,  Neo4j, Docker}}
{2026}
\vspace{-15pt}
\resumeItemListStart

\resumeItem{
Developed a scalable software engineering platform using FastAPI, Node.js, Redis, Neo4j, and Docker to automate repository analysis, code generation, debugging, documentation, and developer workflows.
}

\resumeItem{
Designed scalable backend services with FastAPI, Redis, and Neo4j while implementing memory-enabled reasoning, tool execution, and intelligent agent collaboration for software engineering workflows.
}

\resumeItemListEnd

\vspace{-5pt}
%-------------------------------------------------------------

\resumeProjectHeading
{\textbf{Career Twin– Full-Stack Career Platform}
$|$
\emph{React, Typescript, AWS Bedrock, LangGraph, Vector Search}}
{2026}
\vspace{-15pt}
\resumeItemListStart

\resumeItem{
Developed a full-stack career platform using React, TypeScript, FastAPI, and AWS Bedrock for resume analysis, job matching, and interview preparation.
}

\resumeItem{
Built scalable backend APIs integrating vector search, semantic retrieval, and document processing to deliver personalized career recommendations.
}

\resumeItemListEnd

\vspace{-5pt}
%-------------------------------------------------------------

\resumeProjectHeading
{\textbf{Drone Surveillance Analytics Platform}
$|$
\emph{Python, YOLOv8, OpenCV, LangChain, LLMs, ANFIS, RAG}}
{2026}
\vspace{-13pt}
\resumeItemListStart

\resumeItem{
Developed a modular surveillance analytics platform integrating computer vision inference pipelines with backend processing for drone detection and threat analysis.
}

\resumeItem{
Implemented backend services for surveillance summarization, contextual analytics, and natural language interaction over detection results.
}

\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-13pt}
%------------------------------------
% Research Experience
%------------------------------------

\section{Research Experience}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Real-Time Drone Detection and Classification System}
$|$
\emph{Python, YOLOv8, OpenCV, ANFIS, Fuzzy Logic}}
{2026}
\vspace{-13pt}
\resumeItemListStart

\resumeItem{
Developed a real-time YOLOv8-based drone detection framework with ANFIS-enhanced classification, achieving over 91\% detection accuracy while reducing bird--drone misclassification by 52\%.
}

\resumeItemListEnd
\vspace{-3pt}
%-----------------------------------------------------
\resumeProjectHeading
{\textbf{Generative AI and Agentic Systems Research}
$|$
\emph{LLMs, LangChain, LangGraph, MCP, RAG, AI Agents}}
{Ongoing}
\vspace{-17pt}

\resumeItemListStart

\resumeItem{
Exploring autonomous AI agents, Retrieval-Augmented Generation (RAG), Model Context Protocol (MCP), long-context reasoning, and multi-agent orchestration for enterprise-scale AI applications.
}

\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-13pt}
%------------------------------------
% Technical Skills
%------------------------------------
\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{

\textbf{Programming Languages:}
Python, Java, C++, JavaScript, TypeScript, SQL\\

\textbf{AI \& Machine Learning:}
Scikit-learn, OpenCV, YOLO, Computer Vision, CNNs, Transformers, Vision Transformers,
OpenAI, Gemini, LangChain, LangGraph, RAG, MCP, AI Agents, Embeddings, Vector Search \\

\textbf{Backend Development:}
FastAPI, REST APIs, Node.js, Express.js \\

\textbf{Frontend Development:}
React.js, React Native, HTML, CSS \\ 

\textbf{Databases:}
Neo4j, Redis, PostgreSQL, MongoDB, SQLite, FAISS, Weaviate \\

\textbf{Cloud \& Devops}
AWS, Docker, Kubernetes, Git, GitHub, GitHub Actions, Linux, Azure \\

\textbf{Tools:}
VS Code, Eclipse, Jupyter Notebook, Postman, Linux

}}
\end{itemize}

\vspace{-13pt}
%------------------------------------
% Certifications, Publications & Achievements
%------------------------------------
\section{Certifications \& Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
\item{
\textbf{Research Publications}
Published research papers in international journals and conferences on Computer Vision, Artificial Intelligence, Intelligent Surveillance, Photovoltaic Systems, and Renewable Energy Optimization.

\textbf{Microsoft Certified: Azure AI Fundamentals (AI-900)}
Certified in Azure AI services, Machine Learning fundamentals, Responsible AI, and AI solution development.

\textbf{GATE Qualified}
Qualified GATE Computer Science (2024 \& 2026) and GATE Data Science \& Artificial Intelligence (DA 2026).
}
\end{itemize}

\end{document}