\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%------------------------------------
% Custom Commands
%------------------------------------

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2\\
\textit{\small #3} & \textit{\small #4}\\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2\\
\end{tabular*}\vspace{-7pt}
}
% \newcommand{\resumeProjectHeading}[2]{
%     \item
%     \parbox[t]{0.50\textwidth}{\raggedright\small #1}\hfill
%     \parbox[t]{0.46\textwidth}{\raggedleft\footnotesize\itshape #2}\vspace{-7pt}
% }

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------------------------------
%%%%% RESUME STARTS HERE
%------------------------------------

\begin{document}

%------------------------------------
% Heading
%------------------------------------

\begin{center}
\textbf{\Huge \cshape Vaibhav Kumar Mahawar}\\ \vspace{1pt}

\small +91-8209851728 $|$
\href{mailto:vaibhavmahawar@rocketmail.com}{vaibhavmahawar@rocketmail.com}
$|$
\href{https://www.linkedin.com/in/vaibhavkumarmahawar}{linkedin.com/in/vaibhavkumarmahawar}
$|$
\href{https://github.com/vaibhavmahawar}{github.com/vaibhavmahawar}
\\
Ajmer, Rajasthan, India
\end{center}
\vspace{-15pt}
%------------------------------------
% Education
%------------------------------------

\section{Education}

\resumeSubHeadingListStart

\resumeSubheading
{Dr. B. R. Ambedkar National Institute of Technology Jalandhar}
{Jalandhar, Punjab}
{Master of Technology in Machine Intelligence and Automation \hfill CGPA: 8.11/10}
{Aug. 2024 -- Jun. 2026}

\resumeSubheading
{Poornima Institute of Engineering and Technology}
{Jaipur, Rajasthan}
{Bachelor of Technology in Computer Science and Engineering \hfill \hspace{7pt} CGPA: 8.54/10}
{Jul. 2019 -- Jun. 2023}

\resumeSubHeadingListEnd
\vspace{-10pt}
%------------------------------------
% Experience
%------------------------------------

\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading
{Software Development Intern}
{Jul. 2022 -- Sep. 2022}
{Techienest Pvt. Ltd.}
{Jaipur, Rajasthan}

\vspace{-4pt}
\resumeItemListStart

\resumeItem{
Developed a React Native mobile application for 500+ primary students featuring interactive Vedic mathematics exercises, progress tracking, and REST API integration, improving learning accessibility across Android devices.
}

\resumeItem{
Collaborated with cross-functional teams to develop, test, and optimize scalable mobile application features while integrating REST APIs and improving application performance and maintainability.
}

\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-13pt}
%------------------------------------
% Projects
%------------------------------------

\section{Projects}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Rudra – AI-Powered Software Engineering Platform}
$|$
\emph{Node.js, Typescript, Python, Redis,  Neo4j, Docker}}
{2026}
\vspace{-15pt}
\resumeItemListStart

\resumeItem{
Architected an autonomous multi-agent software engineering platform capable of planning, code generation, repository analysis, debugging, documentation synthesis, and deployment using FastAPI, MCP, and LLM orchestration.
}

\resumeItem{
Designed scalable backend services with FastAPI, Redis, and Neo4j while implementing memory-enabled reasoning, tool execution, and intelligent agent collaboration for software engineering workflows.
}

\resumeItemListEnd

\vspace{-5pt}
%-------------------------------------------------------------

\resumeProjectHeading
{\textbf{Career Twin– AI Career Intelligence Platform}
$|$
\emph{React, Typescript, AWS Bedrock, LangGraph, Vector Search}}
{2026}
\vspace{-15pt}
\resumeItemListStart

\resumeItem{
Developed an AI-driven career intelligence platform that analyzes resumes, matches job descriptions, identifies skill gaps, and generates ATS-optimized resumes, cover letters, and interview preparation plans.
}

\resumeItem{
Implemented semantic retrieval, Retrieval-Augmented Generation (RAG), vector search, and AWS Bedrock-powered reasoning pipelines to deliver personalized career recommendations through scalable backend services.
}

\resumeItemListEnd

\vspace{-5pt}
%-------------------------------------------------------------

\resumeProjectHeading
{\textbf{AI-Powered Drone Intelligence Platform}
$|$
\emph{Python, YOLOv8, OpenCV, LangChain, LLMs, ANFIS, RAG}}
{2026}
\vspace{-15pt}
\resumeItemListStart

\resumeItem{
Developed an AI-powered drone intelligence platform integrating YOLOv8, OpenCV, and ANFIS for real-time drone detection, threat assessment, and explainable decision support across surveillance scenarios.
}

\resumeItem{
Integrated Retrieval-Augmented Generation (RAG) with LLMs to enable natural language querying, surveillance summarization, contextual reasoning, and explainable analysis of detected aerial threats.
}

\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-13pt}
%------------------------------------
% Research Experience
%------------------------------------

\section{Research Experience}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Real-Time Drone Detection and Classification System}
$|$
\emph{Python, YOLOv8, OpenCV, ANFIS, Fuzzy Logic}}
{2026}
\vspace{-13pt}
\resumeItemListStart

\resumeItem{
Developed a real-time YOLOv8-based drone detection framework with ANFIS-enhanced classification, achieving over 91\% detection accuracy while reducing bird--drone misclassification by 52\%.
}

\resumeItemListEnd
\vspace{-3pt}
%-----------------------------------------------------
\resumeProjectHeading
{\textbf{Generative AI and Agentic Systems Research}
$|$
\emph{LLMs, LangChain, LangGraph, MCP, RAG, AI Agents}}
{Ongoing}
\vspace{-17pt}

\resumeItemListStart

\resumeItem{
Exploring autonomous AI agents, Retrieval-Augmented Generation (RAG), Model Context Protocol (MCP), long-context reasoning, and multi-agent orchestration for enterprise-scale AI applications.
}

\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-13pt}
%------------------------------------
% Technical Skills
%------------------------------------
\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{

\textbf{Programming Languages:}
Python, Java, C++, JavaScript, SQL\\

\textbf{AI \& Machine Learning:}
PyTorch, TensorFlow, Scikit-learn, OpenCV, YOLO, Computer Vision, CNNs, Transformers, Vision Transformers, Transfer Learning, ANFIS, Fuzzy Logic \\

\textbf{Generative AI:}
OpenAI, Gemini, LangChain, LangGraph, LlamaIndex, Prompt Engineering, RAG, MCP, AI Agents, Multi-Agent Systems, Tool Calling, Embeddings, Vector Search \\

\textbf{Backend Development:}
FastAPI, REST APIs, Node.js, Express.js \\


\textbf{Databases:}
Neo4j, Redis, PostgreSQL, MongoDB, SQLite, FAISS, Weaviate \\

\textbf{Cloud}
Azure AI, AWS, Docker, Kubernetes, Git, GitHub, GitHub Actions, Linux \\

\textbf{Data Engineering:}
Pandas, NumPy, PySpark, ETL Pipelines, Data Processing, Feature Engineering \\

\textbf{Tools:}
VS Code, Eclipse, Jupyter Notebook, Postman, Linux

}}
\end{itemize}

\vspace{-13pt}
%------------------------------------
% Certifications, Publications & Achievements
%------------------------------------
\section{Certifications \& Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
\item{
\textbf{Research Publications}
Published research papers in international journals and conferences on Computer Vision, Artificial Intelligence, Intelligent Surveillance, Photovoltaic Systems, and Renewable Energy Optimization.

\textbf{Microsoft Certified: Azure AI Fundamentals (AI-900)}
Certified in Azure AI services, Machine Learning fundamentals, Responsible AI, and AI solution development.

\textbf{GATE Qualified}
Qualified GATE Computer Science (2024 \& 2026) and GATE Data Science \& Artificial Intelligence (DA 2026).
}
\end{itemize}

\end{document}