\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%------------------------------------
% Custom Commands
%------------------------------------

\newcommand{\resumeItem}[1]{
  \item\small{
    #1\vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2\\
\textit{\small #3} & \textit{\small #4}\\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2\\
\end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------------------------------
%%%%% RESUME STARTS HERE
%------------------------------------

\begin{document}

%------------------------------------
% Heading
%------------------------------------

\begin{center}
{\Huge \textbf{Vaibhav Kumar Mahawar}}\\[3pt]

+91-8209851728 $|$
\href{mailto:vaibhavmahawar@rocketmail.com}{vaibhavmahawar@rocketmail.com}
$|$
\href{https://www.linkedin.com/in/vaibhavkumarmahawar}{LinkedIn}
$|$
\href{https://github.com/vaibhavmahawar}{GitHub}
\\
Ajmer, Rajasthan, India
\end{center}

%------------------------------------
% Education
%------------------------------------

\section{Education}

\resumeSubHeadingListStart

\resumeSubheading
{Dr. B. R. Ambedkar National Institute of Technology Jalandhar}
{Punjab, India}
{Master of Technology in Machine Intelligence and Automation \hfill CGPA: 8.48/10}
{Aug. 2024 -- Present}

\resumeSubheading
{Poornima Institute of Engineering and Technology}
{Jaipur, Rajasthan}
{Bachelor of Technology in Computer Science and Engineering CGPA: 8.54/10}
{Jul. 2019 -- Jun. 2023}

\resumeSubHeadingListEnd

%------------------------------------
% Experience
%------------------------------------

\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading
{Software Development Intern}
{Jul. 2022 -- Sep. 2022}
{Techienest Pvt. Ltd.}
{Jaipur, Rajasthan}

\resumeItemListStart

\resumeItem{
Developed a React Native mobile application for 500+ primary students featuring interactive Vedic mathematics exercises, progress tracking, and REST API integration, improving learning accessibility across Android devices.
}

\resumeItem{
Collaborated on application testing, debugging, and UI improvements while following software engineering best practices for maintainable and scalable mobile application development.
}

\resumeItemListEnd

\resumeSubHeadingListEnd

%------------------------------------
% Projects
%------------------------------------

\section{Projects}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Rudra AI – Autonomous AI Engineering Platform}
$|$
\emph{Python, FastAPI, React, LangGraph, LangChain, CrewAI, MCP, RAG, Docker}}
{2026}

\resumeItemListStart

\resumeItem{
Developed an autonomous AI engineering platform that assists software developers throughout the SDLC by generating code, debugging issues, analyzing repositories, reviewing pull requests, generating documentation, and automating engineering workflows using multi-agent AI systems.
}

\resumeItem{
Built agentic workflows using LangGraph, LangChain, MCP (Model Context Protocol), Retrieval-Augmented Generation (RAG), tool-calling, and memory-based reasoning to coordinate specialized AI agents.
}

\resumeItem{
Designed scalable backend APIs using FastAPI with modular architecture and integrated modern LLMs for contextual reasoning, code generation, and intelligent software assistance.
}

\resumeItemListEnd


%-------------------------------------------------------------

\resumeProjectHeading
{\textbf{Career Twin – AI Career Intelligence Platform}
$|$
\emph{Python, FastAPI, React, LangChain, LangGraph, Gemini, RAG, Vector Search}}
{2026}

\resumeItemListStart

\resumeItem{
Built an AI-powered career assistant that analyzes resumes, evaluates job descriptions, identifies skill gaps, generates ATS-optimized resumes and cover letters, and provides personalized interview preparation.
}

\resumeItem{
Implemented Retrieval-Augmented Generation (RAG), prompt engineering, semantic retrieval, and structured reasoning pipelines to deliver highly personalized career recommendations and application support.
}

\resumeItem{
Developed modular REST APIs and interactive frontend components enabling intelligent document processing, resume optimization, and conversational AI workflows.
}

\resumeItemListEnd


%-------------------------------------------------------------

\resumeProjectHeading
{\textbf{AI-Powered Drone Intelligence Assistant}
$|$
\emph{Python, YOLOv8, OpenCV, LangChain, LLMs, ANFIS, RAG}}
{2026}

\resumeItemListStart

\resumeItem{
Developed an intelligent surveillance platform integrating YOLOv8-based drone detection with ANFIS-based threat assessment, enabling automated drone analysis from uploaded surveillance videos.
}

\resumeItem{
Integrated LLM-powered conversational analytics using Retrieval-Augmented Generation (RAG) to explain detections, summarize surveillance events, compare results, and answer natural language queries.
}

\resumeItem{
Designed an agentic reasoning workflow combining computer vision, fuzzy logic, structured inference, and LLMs to provide explainable AI-assisted decision support.
}

\resumeItemListEnd

\resumeSubHeadingListEnd

%------------------------------------
% Research Experience
%------------------------------------

\section{Research Experience}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Real-Time Drone Detection and Classification System}
$|$
\emph{Python, YOLOv8, OpenCV, Deep Learning, ANFIS, Explainable AI}}
{2026}

\resumeItemListStart

\resumeItem{
Designed a real-time computer vision framework for autonomous drone detection and tracking using YOLOv8 on large-scale RGB and infrared datasets, achieving over 91\% detection accuracy.
}

\resumeItem{
Improved decision reliability by integrating ANFIS and fuzzy-logic based post-processing, reducing bird--drone misclassification by 52\% while increasing classification robustness under challenging environmental conditions.
}

\resumeItem{
Evaluated the complete pipeline on thousands of surveillance frames and multiple benchmark video sequences, demonstrating improved explainability and real-time inference performance for intelligent surveillance applications.
}

\resumeItemListEnd

%------------------------------------------------------

\resumeProjectHeading
{\textbf{Generative AI and Agentic Systems Research}
$|$
\emph{LLMs, LangChain, LangGraph, MCP, CrewAI, RAG, AI Agents}}
{Ongoing}

\resumeItemListStart

\resumeItem{
Researching Large Language Models, Retrieval-Augmented Generation (RAG), AI Agents, Model Context Protocol (MCP), multi-agent collaboration, and long-context reasoning for enterprise AI applications.
}

\resumeItem{
Experimenting with LangChain, LangGraph, CrewAI, vector databases, prompt engineering, structured tool calling, memory architectures, and autonomous workflow orchestration for intelligent software systems.
}

\resumeItemListEnd

%------------------------------------------------------

\resumeProjectHeading
{\textbf{Publications}
$|$
\emph{Computer Vision, Renewable Energy, Artificial Intelligence}}
{2024--Present}

\resumeItemListStart

\resumeItem{
Published research in international journals and conferences focusing on AI, computer vision, photovoltaic systems, optimization, intelligent surveillance, and renewable energy applications.
}

\resumeItem{
Current research interests include Generative AI, Agentic AI, Computer Vision, Explainable AI, Foundation Models, and intelligent automation systems.
}

\resumeItemListEnd

\resumeSubHeadingListEnd

%------------------------------------
% Technical Skills
%------------------------------------

\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{

\textbf{Programming Languages:}
Python, Java, C++, JavaScript, TypeScript, SQL, C \\

\textbf{AI \& Machine Learning:}
PyTorch, TensorFlow, Scikit-learn, OpenCV, YOLOv8, Computer Vision, Deep Learning, CNNs, Transformers, Vision Transformers, Transfer Learning, ANFIS, Fuzzy Logic \\

\textbf{Generative AI \& LLMs:}
OpenAI GPT, Gemini, LangChain, LangGraph, CrewAI, LlamaIndex, MCP (Model Context Protocol), Prompt Engineering, RAG, AI Agents, Multi-Agent Systems, Tool Calling, Vector Databases, Embeddings \\

\textbf{Backend Development:}
FastAPI, Flask, REST APIs, Node.js, Express.js, Microservices, Authentication, API Integration \\

\textbf{Frontend \& Mobile:}
React.js, React Native, HTML5, CSS3, JavaScript, Flutter \\

\textbf{Databases:}
MongoDB, MySQL, PostgreSQL, SQLite, Vector Databases (Weaviate, FAISS) \\

\textbf{Cloud, DevOps \& MLOps:}
Azure AI, AWS, Google Cloud Platform (GCP), Docker, Kubernetes, Git, GitHub, GitHub Actions, CI/CD, MLflow (Fundamentals) \\

\textbf{Data Engineering:}
Pandas, NumPy, PySpark, ETL Pipelines, Data Processing, Feature Engineering \\

\textbf{Tools:}
VS Code, Jupyter Notebook, Postman, Linux, MATLAB

}}
\end{itemize}

\vspace{-15pt}
%------------------------------------
% Certifications, Publications & Achievements
%------------------------------------

\section{Certifications \& Achievements}

\begin{itemize}[leftmargin=0.15in, label={}]
\small{

\item
\textbf{Research Publications}
Published research papers in international journals and conferences on Computer Vision, Artificial Intelligence, Intelligent Surveillance, Photovoltaic Systems, and Renewable Energy Optimization.

\item
\textbf{Microsoft Certified: Azure AI Fundamentals (AI-900)}
Certified in Azure AI services, Machine Learning fundamentals, Responsible AI, and AI solution development.

\item
\textbf{GATE Qualified}
Qualified GATE Computer Science (2024 \& 2026) and GATE Data Science \& Artificial Intelligence (DA 2026).

\item
\textbf{Research Interests}
Generative AI, Large Language Models, Agentic AI, Retrieval-Augmented Generation (RAG), Computer Vision, Foundation Models, AI Agents, Intelligent Automation, Explainable AI, and Applied Machine Learning.

}
\end{itemize}

\vspace{-8pt}

%------------------------------------
% Publications
%------------------------------------

\section{Publications}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Journal Publications}}{}

\resumeItemListStart

\resumeItem{
Published peer-reviewed research in Computer Vision, Intelligent Surveillance, Photovoltaic Systems, Optimization Algorithms, Artificial Intelligence, and Renewable Energy Applications.
}

\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-10pt}
\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-10pt}

\end{document}